\section{Main Tables for Figures 3-7}
\appendixpagenumbering
\vspace*{.2in}
\setlength{\parskip}{-2em}
%\setlength{\parindent}{1cm}
\doublespacing
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}}	
\renewcommand{\thefigure}{A\arabic{figure}}	

Tables \ref{tab2}- \ref{intermpolempowerment} present coefficient estimates for all models across Figures 3-7 in our main text.  \\

% Fig 3(a) based on Models 1-8
%the main table for forward effect
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA1.tex} %label {tab2}  %index Models 1-8
}

% Fig 3(b-d) based on Models 9 -16
% the types of war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA2.tex} %label {tab3}  % index models 9 -16
}


% Fig 4 based on Models 17-24
% IV model
\begin{landscape}
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA3.tex} %label {ivpolempowerment} % index models 17-24
}
\end{landscape}

% Fig 5(a) based Models 25-32
% war duration and women's empowerment
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA4.tex} %label {polwardur} % index models  25-32
}

%Fig 5(b) based on Models 33-40
% battle deaths
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA5.tex} %label {polbdeath} % index models  33-40
}

% Fig 6(a) based on Models 41-48
% fertility rates
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA6.tex} %label {fefertility} % index models  41-48
}

% Fig 6(b) based on Models 49-56
% fertility rates and existential war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA7.tex} %label {fefertilityexistential} % index models  49-56
}

%Fig 7(a) based on model 57-61
% war on intermediate variable
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA8.tex} %label {FEintermed} % index models  57-61
}

%Fig 7(b-e) based on model 62-69
%  intermediate variables on women's empowerment
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableA9.tex} %label {intermpolempowerment} % index models  62-69
}



\section{Supplementary Tables for Main Results and Figures}
\vspace*{.2in}
\setlength{\parskip}{-2em}
%\setlength{\parindent}{1cm}
\doublespacing
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}}	
\renewcommand{\thefigure}{B\arabic{figure}}	

Tables \ref{fyearonyearpolempower}- \ref{interaction} present additional model specifications to our core models as discussed in the main text.  \\


% Table B1
% Future year-on-year changes in empowerment
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB1.tex} %label {fyearonyearpolempower} % index models  70-77
}

%Table B2
%cumulative death
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB2.tex} %label {culmudeaths} % index models  78-85
}

% Table B3
%New Intrastate war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB3.tex} %label {intrawarpolempower} % index models  86-93
}

% Table B4
%New Interstate war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB4.tex} %label {interwarpolempower} % index models  94-101
}

%Table B5
%new existential war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB5.tex} %label {existentialwarpolempower} % index models  102-109
}

%Table B6
% civil society participation
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB6.tex} %label {fecivilparticip} % index models  110-117
}

% Table B7
% infant mortality and population
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB7.tex} %label {fefertilityinfant} % index models  118-125
}

% Table B8
% Intrastate war and fertility 
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB8.tex} %label {intrawarfertility} % index models  126-133
}

% Table B9
% Interstate war and fertility
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB9.tex} %label {interwarfertility} % index models  134-141
}

% Table B10
% battle deaths and fertility
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB10.tex} %label {fertilitybdeath} % index models  142-149
}

%Table B11
\begin{landscape}
% Military expenditure
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB11.tex} %label {fepolemmilex} % index models  150-158
}
\end{landscape}


% Table B12
% territorial threats w/o war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB12.tex} %label {fepolempnowar} % index models  159-166
}

% Table B13
% territorial threats with war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB13.tex} %label {fepolempnowar} % index models  167-174
}

%Table B14
% Interaction,  *** women's empowerment on the interaction of  the change in power consumption variable and the war variable
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableB14.tex} %label {interaction} % index models  175
}



\section{Robustness Checks and Additional Mechanisms}
\vspace*{.2in}
\setlength{\parskip}{-2em}
%\setlength{\parindent}{1cm}
\doublespacing
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}}	
\renewcommand{\thefigure}{C\arabic{figure}}	

We run several sets of robustness checks to demonstrate that our findings are generally consistent across alternative measures of some key variables and alternative sets of controls. We present the following findings in the Tables \ref{intermedrbst}-\ref{polemprobustsimpyear}. \\

First, we consider the potential for the irregular regime change variable to be highly correlated with the levels and changes in the Polity score included as a control variable. We thus run the models that treat regime change as an intermediate variable without the Polity variables included.\footnote{See Model 176 in Table \ref{intermedrbst}.}  Even when the Polity variables are excluded, we consistently find that war increases the propensity for irregular regime change, which is associated with increases in women's empowerment.\footnote{See Models 178-185 in Table \ref{fepolempnopolity}.} \\

Second, we consider the potential for changes in the Polity score to serve as an intermediate variable.\footnote{See Model 177 in Table \ref{intermedrbst}; and Models 62-69 in Table \ref{intermpolempowerment}.} We find, however, that expected war is not a statistically significant variable that explains changes in Polity scores. Combined with the first robustness check above, it does appear that irregular regime change is capturing a political process that responds to war in ways that are distinct from shifts in the Polity score. Our results also show, consistent with common expectations about the relationship between democratization and gender equality, that Polity-score increases are associated with women's empowerment increases.\\


Polity scores might not adequately control for broader changes and differences in political participation that confound the relationship between war and women's empowerment. Specifically, we consider the possibility that war increases the political engagement of all members of society, not just women, which would undermine the inference that war has gendered social consequences. We thus replace the Polity score variables with two measures from the V-Dem data that capture aspects of democratic governance separate from women's empowerment. The first variable is the {\it civil society index}, which captures civil society robustness---how much individuals enjoy autonomy from the state and are free to pursue their political and civic goals. The second is the {\it clean election index}, defined as the extent to which elections are free and fair. Like the Polity scores, we include both the temporal lags and the first differences.\footnote{See Models 186-193 in Table \ref{fepolempvdem}.} The results confirm that war still is associated with women's empowerment increases even when these alternative controls---which are also associated with gains in women's empowerment---are included. These tests further support the conclusion that war is shaping women's empowerment and not just general political shifts that correlate with women's empowerment.\\


We also consider the possibility that other forms of instability create similar opportunities for women's empowerment. In separate fixed-effects regression models that replace war with {\it national strikes}, {\it government crises}, {\it riots} and {\it mass demonstrations}, we find that both national strikes and mass demonstrations are associated with gains in women's empowerment in the short, medium and long runs.\footnote{See Models 194-201, 202-209, 210-217 and 218-225, in Tables \ref{fepolemstriksnowar}, \ref{polemgovnowar}, \ref{fepolemriotnowar}, and \ref{polemdemonstrationnowar}, respectively. } When war is added in addition to these variables, the medium-term effect of war is robust.\footnote{See Models 26-233 and 234-241 in Tables \ref{fepolemstrikswar} and \ref{polemdemonstrationwar}, respectively. } War shapes gender power dynamics differently than other sources of social upheaval that also appear to open up opportunities for women's empowerment. Further analysis should investigate the mechanisms by which other types of social upheaval contribute to gender power dynamics.\\

We additionally consider whether WWII is a breakpoint in the relationship between war and women's empowerment. We thus run our main  model with an interaction between war and a dummy variable indicator of the post-1946 period.\footnote{See Models 242-249 in Table \ref{fepolemwwII}.} We do not find that the relationship between war and women's empowerment is significantly different in the pre- and post-WWII periods.\\

Finally, we consider a number of additional robustness checks of our main model of types of war on future changes in women's empowerment. In one set of models, we use lagged changes of polity scores and energy consumption to avoid post-treatment bias.\footnote{See Models 250-257 in Table \ref{polemprobustls}.} In another set, we add year fixed effects to further control for cross-panel autocorrelation.\footnote{See Models 258-265 in Table \ref{polemprobustyear}.} In two other sets of models, we check if our results hold in simple models without any control variables but with country fixed effects and, separately, with both country and year fixed effects.\footnote{See Models 266-273, and 274-281 in Tables \ref{polemprobustwocontros} and \ref{polemprobustsimpyear}.} Our main findings hold in each set of models.\\


%Table C1
% irregular without polity, polity as intermediate
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC1.tex} %label {intermedrbst} % index models  176-177
}

%Table C2
% irregular on empowerment without polity
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC2.tex} %label {fepolempnopolity} % index models  178-185
}

% Table C3
% replace polity with V-Dem index
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC3.tex} %label {fepolempvdem} % index models  186-193
}

% Table C4
%{\it national strikes}, {\it government crises}, {\it riots} and {\it mass demonstrations}
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC4.tex} %label {fepolemstriksnowar} % index models  194-201
}

%Table C5
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC5.tex} %label {fepolemgovnowar} % index models  202-209
}

%Table C6
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC6.tex} %label {fepolemriotnowa} % index models  210-217
}

%Table C7
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC7.tex} %label {fepolemdemonstrationnowar} % index models  218-225
}

%Table C8
% add war
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC8.tex} %label {fepolemstrikswar} % index models  226-233
}

%Table C9
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC9.tex} %label {fepolemdemonstrationwar} % index models  234-241
}

% Table C10
% WWII 
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC10.tex} %label {fepolemwwII} % index models  242-249
}

%%%%%%%%%%%%%%%% simple models
%Table C11
% lag of changes in controls
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC11.tex} %label {polemprobustls} % index models  250-257
}

% Table C12
%year fixed effects
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC12.tex} %label {polemprobustyear} % index models  258-265
}

% Table C13
%no control variables
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC13.tex} %label {polemprobustwocontros} % index models  266-273
}
% Table C14
% no controls with year fixed
{\renewcommand\normalsize{\tiny}% adjust table size
	\normalsize
\input{tables/tableC14.tex} %label {polemprobustsimpyear} % index models  274-281
}



\section{Specification of the Endogenous Treatment Effects Regression Model}
\vspace*{.2in}
\setlength{\parskip}{-2em}
%\setlength{\parindent}{1cm}
\doublespacing
\setcounter{table}{0}
\setcounter{figure}{0}


The endogenous treatment-regression model is defined as the simultaneous estimation of the following two equations:
\begin{align}
& \Delta y_{i,t} = \mathbf{z_{i,t}} \beta + \delta x_{i,t} + \epsilon_{i,t} \\
& x_{i,t} = 
 \begin{cases}
 1, & \text{if}\ \mathbf{w_{i,t}} \gamma + \mu_{i,t} >0\\ %``\'' is break
 0, & otherwise
 \end{cases}
\end{align}
where $\Delta y_{i,t}$ is the outcome of interest (here, change in women's empowerment), and $x_{i,t}$ is the endogenous treatment (here, war and instability) for country $i$ at time $t$. Note that $\mathbf{z_{i,t}}$ are the covariates used to model the outcome and $\mathbf{w_{i,t}}$ are the covariates used to model the treatment, and both include time-lagged and change variables as discussed above. The error terms $\epsilon_{i,t}$ and $\mu_{i,t}$ are from the bivariate normal distribution with mean zero and covariance matrix  
\[\begin{bmatrix}
\sigma^2 & \rho \sigma \\
\rho \sigma & 1
\end{bmatrix}.\] \\

